---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%", 
  fig.align = "center",
  fig.dim = c(7,4) * 1.4
)
```

# rjd3nowcasting

<!-- badges: start -->
<!-- badges: end -->

## Overview

Nowcasting is often defined as the prediction of the present, the very near future and the very recent past. 

rjd3nowcasting provides helps to operationalize the process of nowcasting. This first version can be used to specify and estimate dynamic factor models. 
A later version is expected to include the concept of "news" similar to the [Nowcasting plugin](https://github.com/nbbrd/jdemetra-nowcasting/tree/master) 
of the Graphical User Interface of JDemetra+ v2.

## Installation

To get the current stable version (from the latest release):

```{r, echo = TRUE, eval = FALSE}
# install.packages("remotes")
remotes::install_github("rjdemetra/rjd3toolkit@*release")
remotes::install_github("rjdemetra/rjd3nowcasting@*release")
```

To get the current development version from GitHub:

```{r, echo = TRUE, eval = FALSE}
# install.packages("remotes")
remotes::install_github("rjdemetra/rjd3nowcasting")
```


## Usage

```{r, echo = TRUE, eval = TRUE}
library("rjd3nowcasting")
```


### Input

```{r, echo = TRUE, eval = TRUE}
set.seed(100)
data <- ts(
    data = matrix(rnorm(500), 100, 5), 
    frequency = 12, 
    start = c(2010, 1)
)
data[100, 1] <- data[99:100, 2] <- data[(1:100)[-seq(3, 100, 3)], 5] <- NA
```


### Model

```{r, echo = TRUE, eval = TRUE}
dfm_model <- model(
    nfactors = 2,
    nlags = 2,
    factors_type = c("M", "M", "YoY", "M", "Q"),
    factors_loading = matrix(data = TRUE, 5, 2),
    var_init = "Unconditional"
)
```


### Estimation

```{r, echo = TRUE, eval = TRUE}
rslt_ml <- estimate_ml(dfm_model, data)
# or rslt_em<-estimate_em(dfm_model, data)
# or rslt_pca<-estimate_pca(dfm_model, data)
```


### Results

```{r, echo = TRUE, eval = TRUE}
fcst <- get_forecasts(rslt_ml, nf = 2, forecasts_only = TRUE)
params <- get_parameters(rslt_ml)
factors <- get_factors(rslt_ml)
# ...

print(rslt_ml)
summary(rslt_ml)
plot(rslt_ml)
```


## Package Maintenance and contributing

Any contribution is welcome and should be done through pull requests and/or issues.
pull requests should include **updated tests** and **updated documentation**. If functionality is changed, docstrings should be added or updated.


## Licensing

The code of this project is licensed under the [European Union Public Licence (EUPL)](https://joinup.ec.europa.eu/page/eupl-text-11-12).
